Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-12 draft_report.qmd
fixing

|  Cluster  | Number of vaccinations | CHD synthetic prevalence | Rate (No. of vaccinations / CHD synthetic prevalence) | Global rate | Change in number of vaccinations to match global rate |
|:----------:|-----------:|-----------:|:----------:|:----------:|:----------:|
|           |                    *n* |                      *d* |                        *r=n/d*                        | *gr=𝚺n/𝚺d*  |                     *(r-gr) x d*                      |
|     1     |              3,356,002 |                1,026,826 |                         3.27                          |    2.33     |                       -961,239                        |
|     2     |              2,638,698 |                  924,088 |                         2.86                          |    2.33     |                       -483,540                        |
|     3     |              1,862,430 |                  958,825 |                         1.94                          |    2.33     |                       +373,741                        |
|     4     |                476,616 |                  478,728 |                         1.00                          |    2.33     |                       +639,873                        |
|     5     |                332,728 |                  327,542 |                         1.02                          |    2.33     |                       +431,166                        |
| **Total** |          **8,666,474** |            **3,716,009** |                       **2.33**                        |             |                         **0**                         |

>>>>

|  Cluster  | Number of vaccinations | CHD synthetic prevalence | Rate (No. of vaccinations / CHD synthetic prevalence) | Global rate | Change in number of vaccinations to match global rate |
|:---------:|-----------------------:|-------------------------:|:-----------------------------------------------------:|:-----------:|:-----------------------------------------------------:|
|           |                    *n* |                      *d* |                        *r=n/d*                        | *gr=𝚺n/𝚺d*  |                     *(r-gr) x d*                      |
|     1     |              3,356,002 |                1,026,826 |                         3.27                          |    2.33     |                       -961,239                        |
|     2     |              2,638,698 |                  924,088 |                         2.86                          |    2.33     |                       -483,540                        |
|     3     |              1,862,430 |                  958,825 |                         1.94                          |    2.33     |                       +373,741                        |
|     4     |                476,616 |                  478,728 |                         1.00                          |    2.33     |                       +639,873                        |
|     5     |                332,728 |                  327,542 |                         1.02                          |    2.33     |                       +431,166                        |
| **Total** |          **8,666,474** |            **3,716,009** |                       **2.33**                        |             |                         **0**                         |
